\section{Q1-8}
\emph{In the following description, explain when the term account is used as an application domain concept and when as a solution domain concept:}\\
\begin{quote}
Assume you are developing an online system for managing bank accounts for mobile customers.\textsuperscript{1} A major design issue is how to provide access to the accounts when the customer cannot establish an online connection.\textsuperscript{2} One proposal is that accounts are made available on the mobile computer, even if the server is not up.\textsuperscript{3} In this case, the accounts show the amounts from the last connected session.\textsuperscript{4}\\
\end{quote}
(1) \emph{Assume you are developing an online system for managing bank accounts for mobile customers}
\begin{quote}
This sentence is in the application domain, because it does not go in into details with how the system needs to work, but explains system requirements.\\
\end{quote}

(2) \emph{A major design issue is how to provide access to the accounts when the customer cannot establish an online connection.}
\begin{quote}
This is stillin the application domian because it explains problems that the users encounter even without the system.\\
\end{quote}

(3) \emph{One proposal is that accounts are made available on the mobile computer, even if the server is not up.} 
\begin{quote}
This sentence is in the solution domain. It goes into detail as with servers and how the systems can solve a specific problem.\\
\end{quote}

(4) \emph{In this case, the accounts show the amounts from the last connected session.}
\begin{quote}
This sentence is clearly in the solution domain as it explains how a solution in the system can be created.
\end{quote}