\section{Nonfunctional requirements}

In this section is the first draft of the non functional requirements written. It does not include, operation, interface or legal, since these subjects were irrelevant.
\\ 
\\
\HRule \\[0.4cm]
\emph{Usability} \\ 
User must know how to operate a computer and being familiar with the windows interface standard will help, but should not need any training to use the system. Documentation of how to use the program should be included an available in the program. \\
\HRule \\[0.4cm]
\emph{Reliability} \\
Should the system crash, all userdata should still be available on next launch, this could be done by uploading the data to the storage as soon as the user has created or updated it. The system should at worst loose the data concerning an event the user was creating during the crash. Force restarting should not be acceptable and most exceptions must be caught and handled runtime. Data losses cant be 100\% prevented but it must be a focus in the development\\
\HRule \\[0.4cm]
\emph{Performance} \\
The system should be able to hold an large number of events(around 20 events pr day), without slowing the system down with more than 1 second loading in between. Furthermore most user actions must not be met without long waiting times(again up to 1 second), and heawy work should run in the background and thereby not disturbing the user.  The user may have to wait a bit when logging into the system, but no more than 15 seconds with a connection speed of a minimum 2mb down / 2mb up, so the program can retrieve data from the storage. \\
\HRule \\[0.4cm]
\emph{Supportability} \\
Updating by reinstalling is acceptable in this project, but the system should be easy to extent for a programmer.\\
\HRule \\[0.4cm]
\emph{Implementation}\\
The testing will probably be a little scarce due to the small amount of time available to develop the system, but Key components must be tested thoroughly.  The Calendar is a lightweight system, and stores data on the cloud, so there spacewise a maximum of around 1gb should be achievable. Additionally, in it's current form the CalendarSystem is only runnable on Windows OS.\\
\HRule \\[0.4cm]

\newpage